Test-driven Knowledge Graph Construction

### 2023-05-08 doc/paper4.tex
Extract footnote URL

%%
%% end of the preamble, start of the body of the document source.
\begin{document}
%%%URLs in footnotes, that have #
\urldef\urlshacltargets\url{https://www.w3.org/TR/shacl/#targets}
\urldef\urlshaclprebinding\url{https://www.w3.org/TR/shacl/#pre-binding}
\urldef\urlschaclgraphdata\url{https://www.w3.org/TR/shacl/#data-graph}

@@

\textbf{Step 5:} We wrapped the SPARQL queries as SHACL constraints, such as in the example Listing \ref{lst:example-cq} that defines a SPARQL-based constraint component\footnote{\url{https://www.w3.org/TR/shacl/#sparql-constraint-components}} applied to the entire data graph. The \texttt{sh:message} captures the CQ in natural language, which helps to identify which question failed to validate in the validation reports. The \texttt{sh:ask} contains the CQ translated to a SPARQL query prepared in the previous step.

>>>>

%%
%% end of the preamble, start of the body of the document source.
\begin{document}
%%%URLs in footnotes, that have #
\urldef\urlshacltargets\url{https://www.w3.org/TR/shacl/#targets}
\urldef\urlshaclprebinding\url{https://www.w3.org/TR/shacl/#pre-binding}
\urldef\urlschaclgraphdata\url{https://www.w3.org/TR/shacl/#data-graph}
\urldef\urlshaclconstraintcomponent\url{https://www.w3.org/TR/shacl/#sparql-constraint-components}

@@

\textbf{Step 5:} We wrapped the SPARQL queries as SHACL constraints, such as in the example Listing \ref{lst:example-cq} that defines a SPARQL-based constraint component\footnote{\urlshaclconstraintcomponent} applied to the entire data graph. The \texttt{sh:message} captures the CQ in natural language, which helps to identify which question failed to validate in the validation reports. The \texttt{sh:ask} contains the CQ translated to a SPARQL query prepared in the previous step.
